### 2022-01-08 intro.tex
shortened intro

\todo[inline, caption={}]{
    \begin{itemize}
        \item Still missing balance, and too long. Will fix towards the end.
    \end{itemize}
}

@@

The most straightforward approach to experimental research in \acp{NCS} uses setups in which the complete system is built on top of real hardware.
\textcite{Drew2005NCSWLAN} present \iac{NCS} model which considers both random packet delay and loss on both the sensor and actuator sides of the feedback loop; \textcite{Baumann2018LowPower}, on the other hand, develop an evaluation methodology for wireless \ac{NCS}.
Both works validate their results on physical testbeds, consisting of inverted penduli plants controlled wirelessly over IEEE 802.11 WiFi from a central computation point.
Similarly, \textcite{Li2014Wireless} implement a wireless microcontroller-based system for vibration control and validate it on a physical prototype consisting of a cantilever beam controlled over an IEEE 802.15.4 \ac{WPAN} system.
\textcite{Cuenca2019UAV} design and implement periodic event-triggered sampling and dual-rate control techniques for wireless control, validating their contributions on a four-rotor autonomous drone platform controlled over WiFi.

Conversely, some studies choose to instead use completely \emph{simulated} \ac{NCS} setups~\cite{Andersson2005Simulation,Eyisi2012NCSWT}.
Such an approach is employed by \textcite{Du2009Smith}; the authors develop a novel \emph{Smith} predictor to compensate for varying latencies in wireless \acp{NCS} and validate it using the \emph{TrueTime}~\cite{Henriksson2002TrueTime} simulator.
In \textcite{Chen2015synccontrol} the authors validate and evaluate a number of synchronous control strategies for three-motor setups using completely simulated \acp{NCS} environments.
\citeauthor{Wu2012NPC} introduce the concept of \emph{network predictive control} in\ \cite{Wu2012NPC} and use it to balance a simulated inverted pendulum over a simulated wireless network.
In \cite{Ma2019DynamicSched}, \citeauthor{Ma2019DynamicSched} propose an optimal dynamic scheduling strategy that optimizes performance of multi-loop control systems and validate it by simulating a four-loop control system over an IEEE 802.15.4 \ac{WPAN}.

Finally, a number of experimental studies instead employ \emph{hardware-} and \emph{network-in-the-loop} approaches.
Hardware-in-the-loop refers to \ac{NCS} setups in which a real network interacts with a simulated or emulated control system.
This kind of setup is particularly prevalent in the field of \emph{smart grid} control, and has been used by studies such as \textcite{Wang2020VoltageControl}, in which the authors validate a novel three-level coordinated control method for photovoltaic inverters.

On the other hand, network-in-the-loop refers to experimental setups in which the \emph{network} is instead simulated or emulated.
An example of this approach can be found in \textcite{Natale2004InvPendEthernet}, in which the authors interface a real inverted pendulum system with an emulated IEEE 802.3 Ethernet network to study the effects of the \ac{CSMA/CD} medium access control scheme on plant stability.

As evidenced above, experimental research in \acp{NCS} includes a large variety of heterogeneous hardware and software platforms, as well as methodologies and \acp{KPI}.
This, in turn, leads to hardware, software, and methodology fragmentation, as different studies tend to prefer approaches more favored in their respective communities.
Furthermore, existing studies tend to focus on individual aspects and components of a system, thus producing results which do not provide a complete image of the \ac{NCS}.
We identify thus a gap in knowledge pertaining to the reproducibility and comparison of experimental studies on these systems.

@@

Although the work of \textcite{Zoppi2020NCSBench} is a relevant and important step towards the reproducibility of \ac{NCS} benchmarks, we believe it still falls short on some aspects.
In particular, we argue the reliance of \emph{NCSbench} on specific hardware --- accessible as it may be --- hampers the potential of the platform, as it fundamentally limits both the physical systems that can be benchmarked and the scalability of the performed benchmarks.

>>>>

@@

One approach to experimental research in \acp{NCS} uses setups in which the complete system is built on top of real hardware.
This approach is employed in the works of, for instance, \textcite{Drew2005NCSWLAN,Li2014Wireless,Baumann2018LowPower,Cuenca2019UAV}; in all of these, the authors implement and validate their results on physical testbeds of different kinds.
Conversely, some studies choose to instead use completely \emph{simulated} \ac{NCS} setups.
\textcite{Du2009Smith,Wu2012NPC,Chen2015synccontrol,Ma2019DynamicSched} are examples of works in which the authors have opted for such completely virtualized approaches.
These studies often employ combinations of physical and network simulation libraries to try to capture the complex dynamics of \acp{NCS}.
Finally, a number of experimental studies instead employ \emph{hardware-} and \emph{network-in-the-loop} approaches.
Hardware-in-the-loop refers to \ac{NCS} setups in which a real network interacts with a simulated or emulated control system~\cite{Wang2020VoltageControl}.
On the other hand, network-in-the-loop refers to experimental setups in which the \emph{network} is instead simulated or emulated~\cite{Natale2004InvPendEthernet}.

As evidenced above, experimental research in \acp{NCS} includes a large variety of heterogeneous hardware and software platforms, as well as methodologies and \acp{KPI}.
This, in turn, leads to hardware, software, and methodology fragmentation, as different studies tend to prefer approaches more favored in their respective communities.
Furthermore, existing studies tend to focus on individual aspects and components of a system, thus producing results which do not provide a complete image of the \ac{NCS}.
This has caused a gap in knowledge pertaining to the reproducibility and comparison of experimental studies on these systems.

@@

Although the work of \textcite{Zoppi2020NCSBench} is a relevant and important step towards the reproducibility of \ac{NCS} benchmarks, we believe it still falls short on some aspects.
In particular, we argue the reliance of \emph{NCSbench} on specific hardware for the Plant hampers the potential of the platform.
The LEGO Mindstorms platform, although accessible and flexible, still fundamentally limits the physical systems that can be benchmarked to the kind of systems that can be physically implemented on it.
Furthermore, it is \emph{not} scalable, and thus unsuitable for studies of larger, distributed \acp{NCS}.
